Predictive 3D modelling of free oblique cutting of Ti6Al4V titanium alloy and experimental validation for a wide range of conditions\\ \FD{Include AI?}

### 2022-09-14 Article.tex
Revision and comments for the rest of the paper
Now, I need to review the paper according to my comments

A 3-axis GF Mikron VCE 600 Pro milling machine is used to carry out dry free orthogonal and oblique cutting tests on Ti6Al4V (grade 5 annealed at 750°C for 1 h followed by air cooling) with the same kinematics as a shaper. As shown in Figure \ref{ExpSetup}, the tungsten carbide tool (modified LCGN160602-0600-FG, CP500 from SECO) is fixed on a dedicated holder (modified CFHN-06 from SECO) and the sample to be cut is clamped in the spindle (no rotation is allowed during the test). The top of the sample includes 3 ribs of 1 mm in width (width of the tool is 6 mm) and 10 mm in length. The test consists of removing the upper layer (its height is the uncut chip thickness, $h$) of one rib at the prescribed cutting speed, $v_c$. The cutting speed is provided by the feed rate, $v_f$, of the machine (max. value of 40 m/min). The tool cutting edge inclination, $\lambda_s$, results from the relative orientation of the tool and the sample. Forces are measured with a 3-component Kistler 9257B dynamometer and are amplified by a Kistler 5070A charge amplifier. Acquisition is performed at 3 kHz with a Kistler 5697A2 data acquisition system and the DynoWare software. Table \ref{tab:CutCond} shows the cutting conditions, each is repeated 3 times. \FD{Add infos valeur effort: mean, filter, etc. + get info from section 4}

@@

%
\begin{table}[!h]
\begin{center}
\caption{\label{tab:MS} MS sensitivity study (selected $MS_f$ in bold)}
\begin{tabular}{lllll}
\hline\noalign{\smallskip}
$MS_f$  & Speed-up & $\hat{F_c}$ & $\hat{F_f}$ & $\frac{KE}{IE}$ (\%)\\
\noalign{\smallskip}\hline\noalign{\smallskip}
1 & 1 & 1 & 1 & 2.3E-4\\
1E2 & 9 & 1.006 & 0.982 & 2.2E-2\\
\textbf{1E3} & \textbf{21} & \textbf{1.008} & \textbf{0.940} & \textbf{2.2E-1}\\
1E4 & 61 & 1.012 & 0.921 & 2.4\\
1E5 & 173 & Erratic & Erratic & 22\\
1E6 & 207 & Unstable & Unstable & 58\\
\noalign{\smallskip}\hline
\end{tabular}
\end{center}
\end{table}
%

@@

The number of neurons on the hidden layers may influence the results. A sensitivity study on the number of neurons for the first hidden layer is carried out to select the ANN providing the best balance between CPU computation time and quality of the results. The study shows no influence on the forces when compared to the built-in Johnson-Cook model, only computation time is influenced (Table \ref{tab:NbNeurons}). A first hidden layer with 9 neurons is therefore selected.

%
\begin{table}[!h]
\begin{center}
\caption{\label{tab:NbNeurons} Sensitivity to the number of neurons of the first layer, $\zeta$
(selection in bold)}
\begin{tabular}{llll}
\hline\noalign{\smallskip}
$\zeta$  & Time increase (\%) & $\hat{F_c}$ & $\hat{F_f}$\\
\noalign{\smallskip}\hline\noalign{\smallskip}
Built-in & 0 & 1.000 & 1.000\\
\textbf{9} & \textbf{6} & \textbf{1.000} & \textbf{0.999}\\
11 & 6 & 1.001 & 1.000\\
13 & 7 & 1.000 & 0.998\\
15 & 8 & 1.001 & 1.001\\
17 & 10 & 1.000 & 1.000\\
\noalign{\smallskip}\hline
\end{tabular}
\end{center}
\end{table}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental and numerical results\label{sec:ExpNumResults}}
\label{Results}
%%%%%%%%%%%%%%%%%%%%%%%%%%

Experimental and numerical forces are filtered with a second-order low-pass Bessel filter at 750 Hz before computing the mean value of the signal at steady state. Mean and standard deviation ($2\sigma$) are computed from the 3 experimental values and are shown in Figures 5 to 7. Mean numerical values are plotted inside the experimental bars in Figures 5 to 7.

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{Figures/ExpNum_Forces_v10_40µ_6}
\caption{Temporal evolutions of experimental (E) and numerical (N) forces at 6°, 10 m/min and 40 \textmu{}m: dispersion around mean experimental values and linear extrapolation of numerical values in dashed}
\label{ExpNum_Forces_v10_40µ_6}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{Figures/Fx_0}
\caption{Comparison of experimental (E) and numerical (N) cutting forces at 0°}
\label{Fx_0}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

The training of the neural network was performed using a data set containing $3\,430$ data points defined by:
\begin{itemize}
\item $70$ values for $\varepsilon^p\in[0.0,3.0]$, so that $[\varepsilon^p]_{min}=0$ and $[\varepsilon^p]_{max}=3$.
\item $7$ plastic strain rates $\mdot{\varepsilon}^p\in[1, 10, 50, 500, 5\,000, 50\,000, 500\,000]$, so that $[\ln(\mdot{\varepsilon}^p)]_{min}=0$ and $[\ln(\mdot{\varepsilon}^p)]_{max}=13.12236$.
\item  $7$ temperatures $T\in[293, 400, 500, 700, 900, 1\,200, 1\,500]$, so that $[T]_{min}=293$ and $[T]_{max}=1\ 500$.
\end{itemize}

Stresses in the training dataset ranges from $[\sigma]_{min}=171.44$ to $[\sigma]_{max}=2606.12$.
The results of the training process are given below for quantities $\w_1$, $\w_2$, $\overrightarrow{w}$, $\overrightarrow{b_1}$, $\overrightarrow{b_2}$ and $b$.

>>>>

A 3-axis GF Mikron VCE 600 Pro milling machine is used to carry out dry free orthogonal and oblique cutting tests on Ti6Al4V (grade 5 annealed at 750°C for 1 h followed by air cooling) with the same kinematics as a shaper. As shown in Figure \ref{ExpSetup}, the tungsten carbide tool (modified LCGN160602-0600-FG, CP500 from SECO) is fixed on a dedicated holder (modified CFHN-06 from SECO) and the sample to be cut is clamped in the spindle (no rotation is allowed during the test). The top of the sample includes 3 ribs of 1 mm in width (width of the tool is 6 mm) and 10 mm in length. The test consists of removing the upper layer (its height is the uncut chip thickness, $h$) of one rib at the prescribed cutting speed, $v_c$. The cutting speed is provided by the feed rate, $v_f$, of the machine (max. value of 40 m/min). The tool cutting edge inclination, $\lambda_s$, results from the relative orientation of the tool and the sample. Forces are measured with a 3-component Kistler 9257B dynamometer and are amplified by a Kistler 5070A charge amplifier. Acquisition is performed at 3 kHz with a Kistler 5697A2 data acquisition system and the DynoWare software. Table \ref{tab:CutCond} shows the cutting conditions, each is repeated 3 times. \FD{Add infos valeur effort: mean, filter, etc. + get info from section 4: Experimental and numerical forces are filtered with a second-order low-pass Bessel filter at 750 Hz before computing the mean value of the signal at steady state.}

@@

%
\begin{table}[!h]
\begin{center}
\caption{\label{tab:MS} MS sensitivity study (selected $MS_f$ in bold)}\FD{Define $\hat{F_c}$, etc. in caption}
\begin{tabular}{lllll}
\hline\noalign{\smallskip}
$MS_f$  & Speed-up & $\hat{F_c}$ & $\hat{F_f}$ & $\frac{KE}{IE}$ (\%)\\
\noalign{\smallskip}\hline\noalign{\smallskip}
1 & 1 & 1 & 1 & 2.3E-4\\
1E2 & 9 & 1.006 & 0.982 & 2.2E-2\\
\textbf{1E3} & \textbf{21} & \textbf{1.008} & \textbf{0.940} & \textbf{2.2E-1}\\
1E4 & 61 & 1.012 & 0.921 & 2.4\\
1E5 & 173 & Erratic & Erratic & 22\\
1E6 & 207 & Unstable & Unstable & 58\\
\noalign{\smallskip}\hline
\end{tabular}
\end{center}
\end{table}
%

@@

The number of neurons on the hidden layers may influence the results. A sensitivity study on the number of neurons for the first hidden layer is carried out to select the ANN providing the best balance between CPU computation time and quality of the results. The results of the study are provided in Table \ref{tab:NbNeurons}. They show no influence on the forces when compared to the built-in Johnson-Cook model, only computation time is influenced. A first hidden layer with 9 neurons is therefore selected as it leads to the lowest CPU computation time increase.

%
\begin{table}[!h]
\begin{center}
\caption{\label{tab:NbNeurons} Sensitivity of the forces to the number of neurons of the first layer, $\zeta$
(selection in bold)}\FD{Define $\hat{F_c}$, etc. in caption}
\begin{tabular}{llll}
\hline\noalign{\smallskip}
$\zeta$  & Time increase (\%) & $\hat{F_c}$ & $\hat{F_f}$\\
\noalign{\smallskip}\hline\noalign{\smallskip}
Built-in & 0 & 1.000 & 1.000\\
\textbf{9} & \textbf{6} & \textbf{1.000} & \textbf{0.999}\\
11 & 6 & 1.001 & 1.000\\
13 & 7 & 1.000 & 0.998\\
15 & 8 & 1.001 & 1.001\\
17 & 10 & 1.000 & 1.000\\
\noalign{\smallskip}\hline
\end{tabular}
\end{center}
\end{table}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental and numerical results\label{sec:ExpNumResults}}
\label{Results}
%%%%%%%%%%%%%%%%%%%%%%%%%%
\FD{Show chips? + info on side flow? + dedicated subsection on chip thickness?}
Mean and standard deviation ($2\sigma$) are computed from the 3 experimental values and are shown in Figures \hl{5 to 7}. Mean numerical values are plotted inside the experimental bars in Figures \hl{5 to 7}.
\FD{sigma deja utilise mais equa (5) devrait etre sigma y - voir avec Olivier}

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{Figures/ExpNum_Forces_v10_40µ_6}
\caption{Temporal evolutions of experimental (E) and numerical (N) forces at 6°, 10 m/min and 40 \textmu{}m: dispersion around mean experimental values and linear extrapolation of numerical values in dashed}\FD{Style of legend different than text}
\label{ExpNum_Forces_v10_40µ_6}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{Figures/Fx_0}
\caption{Comparison of experimental (E) and numerical (N) cutting forces at 0°}\FD{Better explain legend in caption, same for other figures}
\label{Fx_0}
\end{figure}

@@

\FD{Check clearly stated that Ff trend is globally NOK: improve friction and mat para also cf. Metals Kuga + increase with h quite low in the exp.}
%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\FD{Add biblio}

@@

The training of the neural network was performed using a data set containing $3\,430$ data points defined by: \FD{Add units for min and max values?}
\begin{itemize}
\item $70$ values for $\varepsilon^p\in[0.0,3.0]$, so that $[\varepsilon^p]_{min}=0$ and $[\varepsilon^p]_{max}=3$.
\item $7$ plastic strain rates $\mdot{\varepsilon}^p\in[1, 10, 50, 500, 5\,000, 50\,000, 500\,000]$, so that $[\ln(\mdot{\varepsilon}^p)]_{min}=0$ and $[\ln(\mdot{\varepsilon}^p)]_{max}=13.12236$.
\item  $7$ temperatures $T\in[293, 400, 500, 700, 900, 1\,200, 1\,500]$, so that $[T]_{min}=293$ and $[T]_{max}=1\ 500$.
\end{itemize}

Stresses in the training dataset ranges from $[\sigma]_{min}=171.44$ to $[\sigma]_{max}=2606.12$.
The results of the training process are given below for quantities $\w_1$, $\w_2$, $\overrightarrow{w}$, $\overrightarrow{b_1}$, $\overrightarrow{b_2}$ and $b$.\FD{sigma y?}
